Stability in human interaction networks: primitive typology of vertex, prominence of measures and time activity statistics

### 2015-04-17 paper.tex
terminada adequacao de algumas tabelas

Remarkable features from the analysis of the four email lists are:
\begin{itemize}
    \item The activity along time is practically the same for all lists (Section~\ref{constDisc}) and suggests stable patterns.
    \item The fraction of participants in each Erd\"os sector is stable and can be observed even with very few messages (Section~\ref{subsec:pih}).
    \item The measures combine into principal components in the same way for all lists and all snapshots. 
	    Furthermore, symmetry related measures, defined in this article, present more dispersion than the usual clustering coefficient (Section~\ref{prevalence}).
    \item Typology speculations are immediate from results (Section~\ref{sec:pty}).
\end{itemize}

\begin{table}[!h!]
    \caption{Distribution of activity among agents. First column is dedicated to percentage of messages sent by the most active participant. Column for the first quartile ($1Q$) exhibits minimum percentage of participants responsible for at least 25\% of total messages. Similarly, the column for the first three quartiles $1-3Q$ exhibits minimum percentage of participants responsible for 75\% of total messages. The last decile $-10D$ column has maximum percentage of participants responsible for 10\% of messages.}
\begin{center}
    \begin{tabular}{ | l ||  c | c | c | c | }
        \hline
        list & hub & $ 1Q $ & $ 1-3Q $ & $-10D$ \\ \hline
	\input{tables/userTab}
    \end{tabular}
\end{center}
\label{autores}
\end{table}

The reminder of this section contains a detailed discussion of these results and
Support Information holds tables and figures from which such results can be observed.

@@

There is a concentration of hub activity and of vertex with few connections. Table~\ref{autores} exposes this expected distribution of activity among participants in a scale-free context.

>>>>

Remarkable features from the analysis of the four email lists are:
\begin{itemize}
    \item The activity along time is practically the same for all lists (Section~\ref{constDisc}) and suggests stable patterns.
    \item The fraction of participants in each Erd\"os sector is stable along time and can be observed even with very few messages (Section~\ref{subsec:pih}).
    \item The topological measures (regarded as most basic and still representative for a first analysis) combine into principal components in the same way for all lists and all snapshots. 
	    Furthermore, symmetry related measures, defined in this article, present more dispersion than the usual clustering coefficient (Section~\ref{prevalence}).
    \item Typology speculations are immediate from results (Section~\ref{sec:pty}).
\end{itemize}

The reminder of this section contains a detailed discussion of these results and Support Information holds further tables and figures from which such results can be better observed. The user activity exhibited in Table~\ref{autores} is

@@

There is a concentration of hub activity and of vertex with few connections. Table~\ref{autores} exposes this expected distribution of activity among participants in a scale-free context. As we have seen, one way to observe such distribution of participants is through a comparison of the real network with an Erd\"os R\'enyi model.

\begin{table}[!h!]
    \caption{Distribution of activity among agents. First column presents the percentage of messages sent by the most active participant. Column for the first quartile ($1Q$) exhibits minimum percentage of participants responsible for at least 25\% of total messages. Similarly, the column for the first three quartiles $1-3Q$ exhibits minimum percentage of participants responsible for 75\% of total messages. The last decile $-10D$ column has maximum percentage of participants responsible for 10\% of messages.}
\begin{center}
    \begin{tabular}{ | l ||  c | c | c | c | }
        \hline
        list & hub & $ 1Q $ & $ 1-3Q $ & $-10D$ \\ \hline
	\input{tables/userTab}
    \end{tabular}
\end{center}
\label{autores}
\end{table}
